\section{Development Software}

The tools to create this game are outlined.


\subsection{Game Engine and Programming Language}

The  game  will  be  developed  using either Unreal Engine 4 or the Urho3D  game
engine. It is not yet clear which engine is most suitable. \todo{Choose an engine}

The programming language will primarily be C++.

Below we compare the two engines' capabilities.

\subsubsection*{Urho3D}
\begin{itemize}
    \item \textbf{Supported Platforms}
        Urho3D supports all 3 platforms mentioned, including mobile platforms.
    \item \textbf{Level Editor}
        Urho3D ships with a level editor designed around  the  engine. It can be used by
        artists or programmers to create the worlds the game plays in.
    \item \textbf{On-line Multi-player}
        Urho3D  supports  automatic network synchronization of scene nodes. However,  it
        does not support  client-side  prediction, which is important for a first person
        shooter. This would have to be programmed manually.
    \item \textbf{3D Model Work-flow}
        An  Urho3D  exporter  plugin  exists  for  \textbf{blender}. The models that are
        exported from blender can directly be imported into Urho3D's level editor, along
        with materials. If other 3D modelling  software  besides  blender  is used, then
        Urho3D  is  capable  of  importing  any format supported by the importer library
        \textbf{AssImp}.
\end{itemize}


\subsubsection*{Unreal Engine 4}
\begin{itemize}
    \item \textbf{Supported Platforms}
        UE4 seems to support every platform under the sun, including Windows, Linux, MacOSX, Android \& iOS as well as consoles. 
    \item \textbf{Level Edtiro}
        UE4 ships with a powerful level  editor  designed  around  the engine. It can be
        used  by  artists  or  programmers  to  create  the  worlds the game  plays  in.
    \item \textbf{On-line Multi-player}
        Apparently the engine supports multiplayer out of the box, including client-side prediction
    \item \textbf{3D Model Work-flow}
        UE4 uses .fbx for meshes, which is supported in blender by default. Materials are handled almost entirely within the engine;
        Blender is used only for UV-Mapping.
\end{itemize}


\subsection{3D Modelling Programs}

Any   modelling   program   capable   of   exporting  to  formats  supported  by
\textbf{AssImp} can be used.

\textbf{Blender}  is  the  preferred  modelling  program, as it  is  capable  of
directly exporting to Urho3D's format (if Urho3D is to be chosen as the engine).


\subsection{3D Animation Programs}

Any modellingi program capable of skinned animation can be used.

\textbf{Blender}  is  the  preferred  modelling  program,  as  it  is capable of
directly exporting to Urho3D's format (if Urho3D is to be chosen as the engine).


\subsection{Image Editing Programs}

Any program capable of exporting to common texture formats, such as .PNG or .DDS.


\subsection{Sound and Music Editing Programs}

Any program capable of exporting to common sound/music formats, such as .WAV, .OGG or .MP3.

