\section{Specification}

\subsection{Concept}

\todo[inline]{Lium: Describe the basic concept of this game. What is it? What's it about? What style is the game? What genre is the game? What mechanics (in general) are in this game?}


\subsection{Story}

\todo[inline]{Write about the story (if there is one?) What's the backstory of this game?}


\subsection{Game Structure}

\todo[inline]{What modes of gameplay are there? What does each mode do?}


\subsection{Characters}

\todo[inline]{How many characters are in this game? What are their names? What do they look like? What are their abilities?}


\subsection{Game Mechanics}

\todo[inline]{How does the game work? What abilities *in general* are there? What is the point of the game?}


\subsection{NPCs}

\todo[inline]{Are there NPCs? If so, what are their names? What does each one do? How do they behave? Do they have a backstory?}


\subsection{Items and Pickups}

\todo[inline]{What items exist in the game? How do they affect the player and/or game?}


\subsection{Graphics}

\todo[inline]{What style of graphics are we going for? High detail? Low detail? Cartoon? Realism? What technologies will be incorporated to achieve these graphics? What shaders will we use, what special rendering techniques (if any) will be used?}

\subsubsection{Characters}
\todo[inline]{What is the poly  budget  for  3D  artists?  What  are the texture
resolution  limits?  What  technology/rendering  technique  are  we  using   for
textures?   What   textures   must  exist  on   characters   (diffuse,   normal,
specular,emissive, etc.)? What is the skeleton bone limit? What are the skinning
limits? What world  size  (in  units)  should  characters have? What precautions
should be taken when modelling a character?}

\subsubsection{Props}
\todo[inline]{What is the  poly  budget  for  3D  artists?  What are the texture
resolution   limits?  What  technology/rendering  technique  are  we  using  for
textures? What textures must exist (diffuse, normal, specular,  emissive, etc.)?
What size  (in  units)  should maps have? What other precautions should be taken
when modelling worlds? What is the skeleton bone limit?}


\subsection{Environment}
\todo[inline]{Water? Lava? How are these things implemented?}


\subsection{Items/Pickups}
\todo[inline]{What is the poly budget? Texture resolution limits? etc.}


\subsection{Shaders}
\todo[inline]{What shaders will be used in detail?}


\subsection{Data storage}
\todo[inline]{How are assets organized? What do artists have to look out for?}


\subsection{GUI}
\todo[inline]{How is the graphical user interface structured? What technologies should we use? (Animated buttons or static? etc.)}

